The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-08-02 paper/paper.tex
one more sentence and some spelling

\subsubsection{CosmoDC2}

@@

\begin{figure*}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/nzoverlap_dc2_funbins.pdf}
\caption{The pairwise fractions $f_\mathrm{mis}$ of total objects in redshift regions where multiple tomographic bins contain galaxies, for 
the \textsc{funbins} tomography method and three choices of bands.  
The $x$- and $y$-axes 
show tomographic bin indices, 
and the color represents the fraction of objects (compared to the total number in the challenge) that are 
at redshifts where both tomographic bins have members, in bins of width $\delta z=10^{-3}$.  
This metric corresponds to
the fraction of the area that is shaded in two colours in Figure \ref{fig:funbin_nz}.
The total-overlap figure gives the total fraction of objects
that are ambiguous over all bins, and is the sum of all the pairwise values.}
\label{fig:overlap}
\end{figure*}

@@

One important point to note is that while trained-edge
methods dominate the highest scores for the 3x2pt DETF metric, on which they trained, they
fare much worse on the lensing-only metrics (the methods were not re-trained on the lensing metrics;
we show the metrics for the same assigned bins).  This suggests that the difference between
optimal bins for different science cases is a significant one, and thus that analysis pipelines
should make it straightforward to calibrate multiple configurations and pass them to
subsequent science anlysis; this will probably be true even when comparing models
differing only in their systematic parametrizations.  
This feature is highlighted by the comparison between the two variants
of the \textsc{NeuralNetwork} entry, which differed only in which metric they were targeting;
optimizing one metric does not optimize the other.

>>>>

\subsubsection{CosmoDC2} \label{sec:cosmodc2}

@@

\begin{figure*}[htbp]
% \centering
\includegraphics[width=0.9\linewidth]{results/nzoverlap_dc2_funbins.pdf}
\caption{The pairwise fractions $f_\mathrm{mis}$ of total objects in redshift regions where multiple tomographic bins contain galaxies, for 
the \textsc{funbins} tomography method and three choices of bands.  
The $x$- and $y$-axes 
show tomographic bin indices, 
and the colour represents the fraction of objects (compared to the total number in the challenge) that are 
at redshifts where both tomographic bins have members, in bins of width $\delta z=10^{-3}$.  
This metric corresponds to
the fraction of the area that is shaded in two colours in Figure \ref{fig:funbin_nz}.
The total-overlap figure gives the total fraction of objects
that are ambiguous over all bins, and is the sum of all the pairwise values.}
\label{fig:overlap}
\end{figure*}

@@

One important point to note is that while trained-edge
methods dominate the highest scores for the 3x2pt DETF metric, on which they trained, they
fare much worse on the lensing-only metrics (the methods were not re-trained on the lensing metrics;
we show the metrics for the same assigned bins).  This suggests that the difference between
optimal bins for different science cases is a significant one, and thus that analysis pipelines
should make it straightforward to calibrate multiple configurations and pass them to
subsequent science anlysis; this will probably be true even when comparing models
differing only in their systematic parametrizations.  
This feature is highlighted by the comparison between the two variants
of the \textsc{NeuralNetwork} entry, which differed only in which metric they were targeting;
optimizing one metric does not optimize the other (though the changes between results on the two simulations
could also indicate that this is related to the high-redshift behaviour in the CosmoDC2 simulation
described in \ref{sec:cosmodc2}).
